Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-11-23 LaTeX_paper/paper.tex
Move dataset definition to introduction

\subsection{The Objective Of This Paper}\label{document:objective}
After a review of the existing literature on this problem, some conclusions could be drawn:
The ``digital'' jigsaw puzzle dilemma has been extensively addressed and is already
well-optimized. Conversely, the ``real-world'' counterpart has largely been
overlooked within the academic community.

The first objective for this paper is to fill this void, and been the first formal paper
to analyze the real-world jigsaw puzzle problem.

The second objective is to use the forthcoming research to create a labeling tool.

This objective is motivated by the fact that the biggest challenge for real world puzzles is creating a
reliable comparator~\cref{document:comparator}, that could provide accurate information even with noisy 
input images, that are obtained from real-world measure.

It is easy to see how a machine learning based comparator would probably be the best solution, 
but this poses problems, in fact having to manually scan and label thousands of individual puzzle
pieces to train the model would take ages.
Instead an automatic tool would allow to scan a small $4\times4$ puzzle in one shot,
solve it, and return the labeled data in just minutes.

\section{The Setup}

To fulfill the objectives of this paper,
it is essential to have the necessary data for analysis.
This section will encompass the input data utilized,
as well as the Splitter~\cref{document:splitter}
and Comparator~\cref{document:comparator} algorithms.

\subsection{The Puzzle To Solve}

The first step involves selecting a real-world
puzzle for solving. It has been decided to utilize a
classic 1000-piece puzzle measuring 66cm x 50cm.
A printer's scanner is employed to digitize the individual pieces.

@@

>>>>

\subsection{The Objective Of This Paper}\label{document:objective}

This paper is not the first to tackle the jigsaw puzzle problem in computer science,
in fact there have been several more that are mentioned in the related work section (\cref{document:related_work}).

All the papers we read focused on digital jigsaw puzzles exclusively,
and we couldn't find any paper that mentioned real-world puzzles.
It should be mentioned that we did find some open source project that solved the
real-world puzzle problem, but they didn’t document the creation process nor the
findings given that they weren't trying to write a paper.

This paper’s objective is to focus on both digital and real-world jigsaw puzzles,
and document why the real-world version is harder, and try to quantify by how much.
In other to achieve this objective we want to answer these two questions:
\begin{itemize}
  \item \textbf{What is the difference in execution time between
                digital and real-world puzzles?}

  To answer this question we decided to build a puzzle solver from the ground up,
  and measure his performance across a set of digital, and real-world puzzles.
  Our focus when developing this component wasn't to build a state of the art algorithm,
  as there has already been extensive research put into that;
  We simply needed something that could work with both digital and real-world puzzles.

  \item \textbf{What are the challenges to use the current state of the art algorithms developed for digital
                puzzles in the real-world, and how can we overcome them?}

	Answering this question is a bit trickier, as an algorithm is divided into Comparator~\cref{document:comparator}
  and Solver~\cref{document:solver}. Due to the intrinsic difference of digital and real-world jigsaw puzzles
  reusing the Comparator is impossible, but there is the possibility to reuse the Sover,
  assuming we could build a Comparator for real-world puzzles that is in the same realm
  of accuracy achieved by Comparators for digital puzzles.
  So another way to write this question is: ``Can we build a Comparator for real-world
  puzzles that is accurate enough to work with current state-of-the-art  digital
  puzzle Solvers?''

	To answer this question we will measure the accuracy of the comparator we developed
  to answer the previous question and observe what would happen if that accuracy is
  applied to a digital puzzle solver. We will then propose a solution to improve
  the accuracy of real-world Comparators.

\subsection{The Dataset}
The last step of the introduction is defining our
testing dataset. We need both digital and real world
puzzles to solve. The dataset used, as well as
the code, can be seen in the public GitHub
repository:~\url{https://github.com/lucaSartore/PuzzleSolver}.

\subsubsection{The Real-World Puzzle}
The first step involves selecting a real-world
puzzle for solving. It has been decided to utilize a
classic 1000-piece puzzle measuring 66cm x 50cm.
A printer's scanner is employed to digitize the individual pieces.

@@

\subsubsection{The Digital Puzzle}

\section{Our Implementation Of A Puzzle Solver}
